---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dbSpatial
<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/dbSpatial)](https://CRAN.R-project.org/package=dbSpatial)
<!-- badges: end -->

The goal of `{dbSpatial}` is to provide convenience functions in R for the 
[DuckDB spatial extension](https://duckdb.org/docs/extensions/spatial.html) as well as compatibility with [`{terra}`](https://github.com/rspatial/terra) and other R spatial objects with a DuckDB backend.

## Installation

You can install the development version of dbSpatial from Github like so:

```{r, eval = FALSE}
# install.packages("pak", repos = sprintf("https://r-lib.github.io/p/pak/stable/%s/%s/%s", .Platform$pkgType, R.Version()$os, R.Version()$arch))
pak::pak("ed2uiz/dbSpatial")
```

## Usage
The DuckDB spatial extension can be used with wrapper functions in this package directly (`ST_*()`), through dplyr verbs containing `ST_*()` functions, or SQL queries to a DuckDB database connection containing `ST_*()` functions.
```{r}
library(dbSpatial)

# create duckdb db in memory
duckdb_conn = DBI::dbConnect(duckdb::duckdb(), ":memory:")

# install and load duckdb spatial extension
loadSpatial(conn = duckdb_conn)

# use ST_*() functions directly in R
# TODO

# through dplyr verbs
# TODO

# through SQL queries
# TODO
```


